```{r}
#1question
random_vars <- readRDS("random_vars.rds")

summary(random_vars)

expected_value <- colMeans(random_vars)
variance <- apply(random_vars, 2, var)
standard_deviation <- sqrt(variance)


cat("Expected Value:\n", expected_value, "\n")
cat("Variance:\n", variance, "\n")
cat("Standard Deviation:\n", standard_deviation, "\n")

```

#2question
no we should not comapare standard deviation because standard deviation only represents how disperse is the data but we can comapare corelation which tells us that how the data is interconnected.


#3question

```{r}


cov <- cov(random_vars)
cor <- cor(random_vars)

cat("Covariance Matrix:\n", cov, "\n")
cat("Correlation Matrix:\n", cor, "\n")

```


here the correlation represents that its in high in magnitute so which indicates stronger linear relationship between age and income and covarince indicates the measure of linear dependancy of age and income

#4question
Correlation is a standardized measure that ranges from -1 to 1, it makes easier to compare the strength  and direction of the relationship between variables.

```{r}
#5question

conditional_mean_age_18 <- mean(random_vars$income[random_vars$age <= 18])
conditional_mean_age_18_65 <- mean(random_vars$income[random_vars$age > 18 & random_vars$age < 65])
conditional_mean_age_65 <- mean(random_vars$income[random_vars$age >= 65])


cat("Conditional Expected Value (Age <= 18): ", conditional_mean_age_18, "\n")
cat("Conditional Expected Value (18 < Age < 65): ", conditional_mean_age_18_65, "\n")
cat("Conditional Expected Value (Age >= 65): ", conditional_mean_age_65, "\n")

```